Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election 

### 2024-04-08 paper/paper.qmd
Add files via upload

---
title: "Predicting Participants' Vote Choice Between Conservative and Liberty in the 2025 Election By Binary Linear Regression Model"
title-block-banner: true
abstract: "ojjojojojljk,mkmk."
thanks: "Code and data supporting this analysis are available at: https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
toc: true
toc-depth: 2
number-sections: true
bibliography: references.bib
link-citations: true
---

>>>>

---
title: "Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election "
title-block-banner: true
abstract: "ojjojojojljk,mkmk."
thanks: "Code and data supporting this analysis are available at: https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
toc: true
toc-depth: 2
number-sections: true
bibliography: references.bib
link-citations: true
---
